---
title: "POLS 501: Assignment 6"
date: February 14, 2017
---

Submit your assignment via Canvas. Your submission should consist of two files: an R markdown file and the compiled HTML or PDF file produced by R markdown.

Answer **ONE** of the following two questions.

Start your assignment using this [template](files/assignment6.Rmd).

# The Mathematics of Enigma

*QSS*: Exercise 6.6.1


When calculating factorials and combinations using the functions `lfactorial` and
`lchoose` which calculate the natural logarithm of the factorial ($\log(x!)$) and
binomial coefficient,
$$
\log \choose{n}{k} = \log (n!) - \log(k!) - \log ((n - k)!)
$$
Work with the logarithms of factorials or binomial coefficients since these numbers
get large very quickly, and can result in `Inf` in intermediate calculations.
For example,
```{r}
factorial(1000) / (factorial(998) * factorial(2))
```
doesn't work since `factorial(1000) = Inf`, but can be calculated using log factorials,
```{r}
exp(lfactorial(1000) - lfactorial(998) - lfactorial(2))
```
Even better is to use `lchoose` or `choose` in R, which handle these sorts of numerical issues
in the code,
```{r}
exp(lchoose(1000, 2))
choose(1000, 2)
```
This is a reminder. A good rule of thumb if you don't want to remember too much numerical methods
is to use logarithms whenever you are using really big or really small numbers.
Also, if you ever get `Inf` in a calculation, switch to the log scale.

For part 5: an alternate approach is to return a 13 x 2 data frame.
Then in part 6, expand it to a 52 x 2 data frame that maps all upper and lower
case letters to their encoded value.
Then join this data frame to a data frame with one column with in which each row is
a letter of the method. ...

For part 6: the **stringr** function equivalents are

- `str_replace` and `str_replace_all` to replace patterns
- `str_to_upper` and `str_to_lower`
- `str_split(x, "")[[1]]` will split a length one character vector with `n` characters into a
   character vector of length `n` in which each element is a character.

```{r}
library("stringr")
letters
alphabet <- str_c(letters, collapse = "")
alphabet
str_split(alphabet, "")[[1]]
```

# Election Fraud in Russia

*QSS* Exercise 6.6.3
