---
title: Schedule
---

```{r include=FALSE, results='hide', message = FALSE}
library("tidyverse")
library("lubridate")
library("stringr")
library("yaml")
library("htmltools")
library("commonmark")
knitr::opts_chunk$set(echo = FALSE)
schedule <- yaml.load_file("schedule.yaml")
```


> "No plan survives contact with the enemy"
> --- paraphrased quote of [Helmuch von Moltke the Elder](https://en.wikiquote.org/wiki/Helmuth_von_Moltke_the_Elder)


This schedule is an approximation, subject to change due needs of the students in the course.
Students will be informed of changes to the schedule.


# Research Project

Prior to the final paper being due there will be approximately weekly assignments in order to provide feedback, and allow you to immediately implement concepts and methods learned in the course.

See [research project](research_project.html) page for instructions.

<table class="table table-stripped">
<thead>
<th>Assignment</th>
<th>Due date </th>
</thead>
<tbody>
```{r echo = FALSE,results='asis'}
map(
  schedule[["research_project"]],
  function(row) {
  withTags(
    tr(
      td(tags$a(row[["name"]],
           href = str_c("research_project.html#", row[["href"]]))
         ),
      td(time(format(ymd_hm(row[["date"]]), "%b %d %H:%M (%a)")),
         datetime = format(ymd_hm(row[["date"]]), "%Y-%m-%dT%H:%M"))
    )
  )
  }
) %>% tagList()
```
</tbody>
</table>

# Assignments

<table class="table table-stripped">
<thead>
<th>Assignment</th>
<th>Due date </th>
</thead>
<tbody>
```{r echo = FALSE,results='asis'}
map2(
  seq_along(schedule[["assignments"]]),
  schedule[["assignments"]],
  function(i, x) {
    .date <- ymd_hm(x[["date"]])
    tags$tr(
      tags$td(tags$a(str_c("Assignment ", i),
                     href = str_c("assignment-", i, ".html"))),
      tags$td(tags$a(tags$time(format(.date, "%b %d %H:%M (%a)"),
                               datetime = format(.date, "%Y-%m-%dT%H:%M:00")),
                     href = x[["canvas"]]))
    )
  }
) %>% tagList()
```
</tbody>
</table>


# Readings, Assignments, Lectures

Abbreviations used in the schedule:

- *r4ds*: Wickham and Groelmund, [R for Data Science](http://r4ds.had.co.nz/)
- *QSS*: Imai, *A First Course in Quantitative Social Science*
- *OpenIntro*: [OpenIntro Statistics, 3rd edition](https://www.openintro.org/stat/textbook.php?stat_book=os)
- *RealStats*: Bailey, *Real Stats*

```{r}
render_week <- function(x) {
  w <- x[["week"]]
  classes <-  map(x[["classes"]], render_class)
  hdr <- tags$h2(a(`data-toggle` = "collapse",
                    href = str_c("#collapse", w),
                    str_c("Week ", w)),
                  id = str_c("week-", w),
                  class = "panel-title")
  div(class = "panel-group",
      div(class = "panel panel-default",
          div(class = "panel-heading", hdr),
          div(id = str_c("collapse", w), class = "panel-collapse collapse",
              classes)
      )
  )
             
}

class_type <- function(x) {
  if (.wday == 3) { # Tues
    "Lecture"
  } else if (.wday == 6) { # Friday
    "Lab"
  } else {
    stop(format(.date, "%Y-%m-%d"), " is neither a Tuesday nor a Friday.",
         call. = FALSE)
  }
}

render_reading <- function(x) {
  tags$li(HTML(commonmark::markdown_html(x)))
}

render_readings <- function(x) {
  tags$ul(map(x, render_reading))
}

render_class <- function(x) {
  .date <- ymd(x[["date"]])
  .wday <- wday(.date)
  .header <- h3(tags$time(format(.date, "%a, %b %d, %Y"),
                          datetime = format(.date, "%Y-%m-%d")),
                id = format(.date, "%Y-%m-%d"))
  inclass <- if (!is.null(x[["inclass"]])) {
    list(h4("In class", id = str_c("inclass-", format(.date, "%Y-%m-%d"))),
         render_readings(x[["inclass"]]))
  } else {
    NULL
  }
  readings <- if (!is.null(x[["readings"]])) {
    list(h4("Readings", id = str_c("readings-", format(.date, "%Y-%m-%d"))),
         render_readings(x[["readings"]]))
  } else {
    NULL
  }
  extras <- if (!is.null(x[["extras"]])) {
    list(h4("Additional Resources", id = str_c("extras-", format(.date, "%Y-%m-%d"))),
         render_readings(x[["extras"]]))
  } else {
    NULL
  }
  tagList(.header, inclass, readings, extras)
}

tagList(map(schedule[["weeks"]], render_week))
```

