---
title: "Assignment 4"
author: "Jeffrey Arnold"
date: "2/7/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

For help with R Markdown see:

- [R for Data Science chapter](http://r4ds.had.co.nz/r-markdown.html)
- Click on the menu `Help > Markdown Quick Reference` for Markdown syntax
- [R Markdown Cheat Sheet](https://www.rstudio.com/resources/cheatsheets/) and
  [R Markdown Reference Guide](https://www.rstudio.com/wp-content/uploads/2015/03/rmarkdown-reference.pdf); available via the menu `Help > Cheatsheets` in RStudio.
- [RStudio R Markdown site](http://rmarkdown.rstudio.com/) for more detailed info


## Prerequisites

Load any packages that you use here:
```{r message=FALSE}
library("tidyverse")
library("modelr")
library("broom")
```


## Election and Conditional Cash Transfer Program in Mexico

This problem is from *QSS*: Exercise 4.5.2, parts 1 and 2

The data for this problem is the 
```{r}
QSS_GITHUB_URL <- "https://raw.githubusercontent.com/kosukeimai/qss/master/"
progresa_url <- str_c(QSS_GITHUB_URL, "PREDICTION/progresa.csv")
                      
col_types <- cols(
  .default = col_double(),
  treatment = col_integer(),
  pri1994 = col_integer(),
  pan1994 = col_integer(),
  prd1994 = col_integer(),
  votos1994 = col_integer(),
  pobtot1994 = col_integer(),
  villages = col_integer()
)
progresa <- read_csv(progresa_url, col_types = col_types)
```

### Part 1

Answer here

### Part 2

Answer here

